---
title: "Example Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(ggridges)
library(plotly)
library(reactable)

theme_set(theme_classic())

wide <- read_csv('C:/Users/cpppe/Desktop/github_projects/gradschool_dashboard/data/wide_data.csv') %>% 
  filter(year == 18) %>% 
  dplyr::select(-X1)

wide <- wide %>% 
  mutate(credit_per_class = credit/headcount,
         credit_per_full_num = case_when(credit_per_class < 2 ~ 1,
                                      credit_per_class >= 2 & credit_per_class < 3 ~ 2,
                                      credit_per_class >= 3 & credit_per_class < 4 ~ 3,
                                      credit_per_class >= 4 & credit_per_class < 5 ~ 4,
                                      credit_per_class >= 5 & credit_per_class < 6 ~ 5,
                                      credit_per_class >= 6 & credit_per_class < 7 ~ 6,
                                      credit_per_class >= 7 & credit_per_class < 8 ~ 7,
                                      credit_per_class >= 8 & credit_per_class < 9 ~ 8,
                                      credit_per_class >= 9 & credit_per_class < 10 ~ 9,
                                      credit_per_class >= 10 & credit_per_class < 11 ~ 10,
                                      credit_per_class >= 11 & credit_per_class < 12 ~ 11,
                                      credit_per_class >= 12 & credit_per_class < 13 ~ 12,
                                      credit_per_class >= 13 & credit_per_class < 14 ~ 13,
                                      credit_per_class >= 14 & credit_per_class < 15 ~ 14,
                                      credit_per_class == 15 ~ 15)) %>% 
  filter(course_level == 'Undergraduate')

wide <- wide %>% 
  sample_frac(.05)
```

University of Oregon
=======================================================================

Inputs {.sidebar}
-----------------------------------------------------------------------
This should be an explanation of the first page as well as the plots for the following tabs (each college).  

Column {data-width=600}
-----------------------------------------------------------------------

### Density of GEs Across the Colleges

```{r}
stu <- c('Doctoral' = '#669b3e', 'Law' = '#398b98', 'Masters' = '#ea5227')

wide %>%
  filter(ge == 1) %>% 
  pivot_longer(cols = c(5, 7, 9, 11),
               names_to = 'fte_ge',
               values_to = 'amount_fte') %>% 
    filter(fte_ge == 'ge_admin_fte' |
           fte_ge == 'ge_rsch_fte' |
           fte_ge == 'ge_teach_fte') %>% 
  mutate(college = recode(college, 'School of Music & Dance' = 'SOMD',
                          'School of Law' = 'LAW',
                          'School of Journalism & Communication' = 'SOJC',
                          'Lundquist College of Business' = 'LCOB',
                          'College of Education' = 'COE',
                          'College of Design' = 'COD',
                          'College of Arts & Sciences' = 'CAS'),
         fte_ge = recode(fte_ge, 'ge_admin_fte' = 'Administration GE',
                         'ge_rsch_fte' = 'Research GE',
                         'ge_teach_fte' = 'Teaching GE')) %>% 
  drop_na(college, student_level) %>% 
  ggplot(aes(x = amount_fte, y = college, fill = student_level)) +
  geom_density_ridges(alpha = .4, color = 'gray70', scale = .85) +
  facet_wrap(~fte_ge, ncol = 3) +
  scale_x_continuous(breaks = c(.2, .4, .49),
                     limits = c(.1, .60)) +
  geom_vline(linetype = 1, xintercept = .2, size = .5, alpha = .5) +
  geom_vline(linetype = 2, xintercept = .4, size = .5, alpha = .5) +
  geom_vline(linetype = 3, xintercept = .49, size = .5, alpha = .5) +
  labs(x = 'Amount of GE FTE',
       y = 'College',
       fill = 'Student Level',
       title = 'Density of Different Graduate Employment (GE) types by College',
       caption = 'Note. .2, .4, and .49 are the most common GE full-time equivalent (FTE) values\n
       SOMD = School of Music & Dance; SOJC = School of Journalism & Communication\n
       LCOB = Lundquist College of Business; LAW = Law School\n
       COE = College of Education; COD = College of Design\n
       CAS = College of Arts & Sciences') +
  scale_fill_manual(values = stu) +
  theme(legend.position = 'bottom')
```

Column {data-width=400}
-----------------------------------------------------------------------

### Average FTE for GEs Across Colleges & Departments

```{r}
mean_fte_plot <- wide %>% 
  filter(ge_teach == 1 &
           college != 'Graduate School') %>% 
  group_by(course_dept, ge_teach) %>%
  mutate(mean_fte = mean(ge_teach_fte),
         ge_teach_n = n()) %>%
  ungroup() %>%
  ggplot(aes(college, mean_fte, size = ge_teach_n)) +
  geom_point(aes(color = course_dept)) +
  coord_flip() +
  scale_y_continuous(breaks = c(.2, .3, .4, .5),
                     limits = c(.2, .5)) +
  labs(x = 'Mean Teaching FTE',
       y = ' ') +
  theme(legend.position = 'none') +
  scale_color_manual(values = c('#5e2228', '#d22a2c', '#9b2a30', '#c80010',
                     '#6a1f25', '#d72d2b', '#5b2c2f', '#387448',
                     '#c0c5ba', '#888980', '#344039', '#4f4c3c',
                     '#807f67', '#386350', '#387448', '#5b6242',
                     '#669b3e', '#808572', '#7fb7b7', '#53636b',
                     '#85b3c1', '#507b8b', '#2c6195', '#4b5f71',
                     '#4b5f71', '#3f6698', '#26657f', '#398b98',
                     '#ddca72', '#c3b37d', '#d3bb95', '#c4bb9b',
                     '#a26540',
                     '#dbd5a5', '#a86428', '#c7a860', '#c0cc56', 
                     '#e5e1d4', '#d3bb95', '#a26540', '#ead568',
                     '#7f5d47', '#b23a2d', '#c33431', 'd74122',
                     '#b23a2d'))

ggplotly(mean_fte_plot) %>% 
  partial_bundle()
```

Colleges
=======================================================================

Column {.tabset}
-----------------------------------------------------------------------

### College of Arts & Sciences

```{r}
cas_scat <- wide %>% 
  filter(college == 'College of Arts & Sciences' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_point(aes(color = as.factor(course_dept)), alpha = .7) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE) +
  theme(legend.position = 'none') 
  # scale_color_manual(values = c('#5e2228', '#d22a2c', '#9b2a30', '#c80010',
  #                    '#6a1f25', '#d72d2b', '#5b2c2f', '#387448',
  #                    '#c0c5ba', '#888980', '#344039', '#4f4c3c',
  #                    '#807f67', '#386350', '#387448', '#5b6242',
  #                    '#669b3e', '#808572', '#7fb7b7', '#53636b',
  #                    '#85b3c1', '#507b8b', '#2c6195', '#4b5f71',
  #                    '#4b5f71', '#3f6698', '#26657f', '#398b98',
  #                    '#ddca72', '#c3b37d', '#d3bb95', '#c4bb9b',
  #                    '#a26540',
  #                    '#dbd5a5', '#a86428', '#c7a860', '#c0cc56', 
  #                    '#e5e1d4', '#d3bb95', '#a26540', '#ead568',
  #                    '#7f5d47', '#b23a2d', '#c33431', 'd74122',
  #                    '#b23a2d'))

ggplotly(cas_scat) %>% 
  partial_bundle()
```

### College of Design

```{r}
wide %>% 
  filter(college == 'College of Design' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_point(aes(color = as.factor(course_dept)), alpha = .7) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE) +
  # scale_color_manual(values = c('#669b3e', '#398b98', '#ea5227', '#d72d2b', '#4b5f71')) +
  theme(legend.title = element_blank())

```

### College of Education

```{r}
wide %>% 
  filter(college == 'College of Education' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_point(aes(color = as.factor(course_dept)), alpha = .5) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE) +
  # scale_color_manual(values = c('#669b3e', '#398b98', '#ea5227', '#d72d2b')) +
  theme(legend.title = element_blank())

```

### Lundquist College of Business

```{r}
wide %>% 
  filter(college == 'Lundquist College of Business' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_point(aes(color = as.factor(course_dept)), alpha = .5) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE) +
  # scale_color_manual(values = c('#398b98')) +
  theme(legend.title = element_blank())

```

### School of Journalism & Communication

```{r}
wide %>% 
  filter(college == 'School of Journalism & Communication' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_point(aes(color = as.factor(course_dept)), alpha = .5) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE) +
  # scale_color_manual(values = c('#398b98')) +
  theme(legend.title = element_blank())

```

### School of Law

```{r}
wide %>% 
  filter(college == 'School of Law' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_point(aes(color = as.factor(course_dept)), alpha = .5) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE) +
  # scale_color_manual(values = c('#398b98')) +
  theme(legend.title = element_blank())

```

### School of Music & Dance

```{r}
wide %>% 
  filter(college == 'School of Music & Dance' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_point(aes(color = as.factor(course_dept)), alpha = .5) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE) +
  # scale_color_manual(values = c('#398b98')) +
  theme(legend.title = element_blank())

```

Column (.tabset)
-----------------------------------------------------------------------

### Average GE Teaching FTE & Undergraduate Course Credits
```{r}
wide %>% 
  filter(ge_teach == 1) %>% 
  drop_na(ge_teach, ge_teach_fte, credit) %>% 
  group_by(college, course_dept, ge_teach) %>%
  summarize(mean_fte = mean(ge_teach_fte),
         `GE Teaching Observations` = n(),
         mean_credit = mean(credit),
         `Average GE Teaching FTE` = round(mean_fte, 3),
         `Average Student Credit Hours` = round(mean_credit, 3)) %>% 
  rename(College = college,
         `Course Department` = course_dept) %>% 
  ungroup() %>% 
  dplyr::select(College, `Course Department`, `GE Teaching Observations`, `Average GE Teaching FTE`,
                `Average Student Credit Hours`) %>% 
  reactable::reactable()

```

### Correlation Between Teaching GE FTE & Undergraduate Course FTE

```{r}
beta_func <- function (object){
    if (!"lm" %in% attr(object, "class")) 
        stop("object has to be of class lm")
    object$standardized.coefficients <- coef(object) * apply(as.matrix(model.matrix(object)), 
        2, function(x) sqrt(sum((x - mean(x, na.rm = T) * attr(attr(object$model, 
            "terms"), "intercept"))^2, na.rm = T)))/apply(as.matrix(model.frame(object)[, 
        1]), 2, function(x) sqrt(sum((x - mean(x, na.rm = T) * 
        attr(attr(object$model, "terms"), "intercept"))^2, 
        na.rm = T)))
    # attr(object, "class") <- c("lm.beta", "lm")
    return(object)
}

wide_lm_list <- wide %>% 
  drop_na(college, course_dept, credit, ge_teach_fte) %>% 
  group_by(college, course_dept) %>% 
  nest() %>% 
  mutate(lm_model = map(data, ~lm(credit ~ ge_teach_fte, data = .x)),
         lm_coefs = map(lm_model, coef),
         ge_teach_fte_b = map_dbl(lm_coefs, 2),
         betas = map_dbl(lm_model, ~beta_func(.x)$standardized.coefficients[2]),
         lm_r2 = map_dbl(lm_model, ~summary(.x)$r.squared),
         lm_pvalue = map_dbl(lm_model, ~summary(.x)$coefficients[, 4]['ge_teach_fte']),
         lm_r = map_dbl(lm_r2, ~sqrt(.x)))

wide_lm_list %>% 
  dplyr::select(college, course_dept, ge_teach_fte_b, betas, lm_pvalue) %>% 
  rename(`College` = college,
         `Course Department` = course_dept) %>% 
  mutate(b = round(ge_teach_fte_b, digits = 3),
         beta = round(betas, digits = 3), 
         `p value` = round(lm_pvalue, digits = 3)) %>% 
  dplyr::select(-ge_teach_fte_b, -lm_pvalue, -betas) %>% 
  reactable::reactable()
```

