---
title: "Synthetic Data for the University of Oregon"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(ggridges)
library(ggpubr)
library(plotly)
library(reactable)

theme_set(theme_classic())

colleges_combined <- function(percent){
  
  cas <- readr::read_csv('https://media.githubusercontent.com/media/jpedroza1228/gradschool_dashboard/main/synthetic_data/synthetic_csv/Arts_Sciences_synthetic.csv') %>% 
    mutate(college = 'College of Arts & Sciences') %>% 
    dplyr::sample_frac(percent)
  bus <- readr::read_csv('https://media.githubusercontent.com/media/jpedroza1228/gradschool_dashboard/main/synthetic_data/synthetic_csv/Business_synthetic.csv') %>% 
    mutate(college = 'Lundquist College of Business') %>% 
    dplyr::sample_frac(percent)
  des <- readr::read_csv('https://media.githubusercontent.com/media/jpedroza1228/gradschool_dashboard/main/synthetic_data/synthetic_csv/Design_synthetic.csv') %>% 
    mutate(college = 'College of Design') %>% 
    dplyr::sample_frac(percent)
  coe <- readr::read_csv('https://media.githubusercontent.com/media/jpedroza1228/gradschool_dashboard/main/synthetic_data/synthetic_csv/Education_synthetic.csv') %>% 
    mutate(college = 'College of Education') %>% 
    dplyr::sample_frac(percent)
  sojc <- readr::read_csv('https://media.githubusercontent.com/media/jpedroza1228/gradschool_dashboard/main/synthetic_data/synthetic_csv/Journalism_Communication_synthetic.csv') %>% 
    mutate(college = 'School of Journalism & Communication') %>% 
    dplyr::sample_frac(percent)
  law <- readr::read_csv('https://media.githubusercontent.com/media/jpedroza1228/gradschool_dashboard/main/synthetic_data/synthetic_csv/Law_synthetic.csv') %>% 
    mutate(college = 'School of Law') %>% 
    dplyr::sample_frac(percent)
  mus <- readr::read_csv('https://media.githubusercontent.com/media/jpedroza1228/gradschool_dashboard/main/synthetic_data/synthetic_csv/Music_Dance_synthetic.csv') %>% 
    mutate(college = 'School of Music & Dance') %>% 
    dplyr::sample_frac(percent)
  
  joined <- dplyr::full_join(cas, bus) %>% 
    dplyr::full_join(des) %>% 
    dplyr::full_join(coe) %>% 
    dplyr::full_join(sojc) %>% 
    dplyr::full_join(law) %>% 
    dplyr::full_join(mus)
  
  message('This is synthetic data for all UO Colleges/Schools')
  
  return(joined)
}

set.seed(123654)
uo <- colleges_combined(percent = .01)

```

University of Oregon
=======================================================================

Inputs {.sidebar}
-----------------------------------------------------------------------
This dashboard is for those in the Graduate School that are interested in the average teaching graduate employment (GE) full-time equivalency (FTE), distribution of various types of GE opportunities across the University of Oregon (UO), and the correlations between GE teaching FTE and student credit hours. 

Synthetic data can be found [here](https://github.com/jpedroza1228/gradschool_dashboard/tree/main/synthetic_data/synthetic_csv)

**Common terms used in all visuals and tables**\n

CAS = College of Arts & Sciences\n

COD = College of Design\n

COE = College of Education\n

LCOB = Lundquist College of Business\n

SOJC = School of Journalism & Communication\n

LAW = Law School\n

SOMD = School of Music & Dance\n

GE = Graduate Employment\n

FTE = Full-time Equivalency\n

UO = University of Oregon\n


Column {data-width=600}
-----------------------------------------------------------------------

### Average FTE for GEs Across Colleges & Departments

```{r}
uo %>% 
  filter(ge_teach == 1) %>% 
  group_by(course_dept) %>%
  mutate(mean_fte = mean(ge_teach_fte),
         mean_fte = round(mean_fte, digits = 3),
         ge_teach_n = n(),
         college = recode(college, 'School of Music & Dance' = 'SOMD',
                          'School of Law' = 'LAW',
                          'School of Journalism & Communication' = 'SOJC',
                          'Lundquist College of Business' = 'LCOB',
                          'College of Education' = 'COE',
                          'College of Design' = 'COD',
                          'College of Arts & Sciences' = 'CAS')) %>%
  ungroup() %>%
  ggplot(aes(fct_reorder(course_dept, mean_fte), mean_fte)) +
  geom_col(position = 'dodge', aes(fill = college)) +
  # geom_point(aes(color = college)) +
  geom_text(aes(label = mean_fte), hjust = 1, size = 2.75) +
  geom_text(aes(label = college, y = .03),
            position = position_dodge(width = .5),
            size = 2.75) +
  scale_y_continuous(limits = c(0, .5),
                     expand = c(0, 0)) +
  scale_fill_manual(values = c('#FFF6B7','#8CD4C9', '#F7471A', '#D1E6F2', '#23A1E3', '#AA1818', '#601a35')) +
  coord_flip() +
  labs(title = 'Average Teaching FTE Across Departments at UO',
       caption = '',
       x = ' ',
       y = 'Average GE Teaching FTE') +
  theme(legend.position = 'none',
        axis.text.y = element_text(size = 8))

```

Column {data-width=400}
-----------------------------------------------------------------------

### Density of GEs Across the Colleges

```{r}
stu <- c('Doctoral' = '#669b3e', 'Law' = '#398b98', 'Masters' = '#ea5227')

uo %>%
  filter(ge == 1) %>% 
  pivot_longer(cols = c(8, 10, 12),
               names_to = 'fte_ge',
               values_to = 'amount_fte') %>% 
  mutate(college = recode(college, 'School of Music & Dance' = 'SOMD',
                          'School of Law' = 'LAW',
                          'School of Journalism & Communication' = 'SOJC',
                          'Lundquist College of Business' = 'LCOB',
                          'College of Education' = 'COE',
                          'College of Design' = 'COD',
                          'College of Arts & Sciences' = 'CAS'),
         fte_ge = recode(fte_ge, 'ge_admin_fte' = 'Administration GE',
                         'ge_rsch_fte' = 'Research GE',
                         'ge_teach_fte' = 'Teaching GE')) %>% 
  drop_na(college, student_level) %>% 
  ggplot(aes(x = amount_fte, y = college, fill = student_level)) +
  geom_density_ridges(alpha = .3, color = 'gray70', scale = .8) +
  facet_wrap(~fte_ge, ncol = 3) +
  scale_x_continuous(breaks = c(.2, .4, .49),
                     limits = c(.1, .60)) +
  geom_vline(linetype = 1, xintercept = .2, size = .5, alpha = .5) +
  geom_vline(linetype = 2, xintercept = .4, size = .5, alpha = .5) +
  geom_vline(linetype = 3, xintercept = .49, size = .5, alpha = .5) +
  labs(x = 'Amount of GEs at varying FTE',
       y = ' ',
       fill = 'Student Level',
       title = 'Density of Different GE types by College',
       caption = 'Note. .2, .4, and .49 are the most common GE FTE values') +
  scale_fill_manual(values = stu) +
  theme(legend.position = 'bottom')

```

Colleges {data-orientation=rows}
=======================================================================

Row {.tabset}
-----------------------------------------------------------------------

### College of Arts & Sciences

```{r}

cas_p_static <- uo %>% 
  filter(college == 'College of Arts & Sciences' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_jitter(aes(color = as.factor(course_dept)), alpha = .1) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE, size = 1) +
  theme(legend.position = 'none') +
  scale_color_manual(values = c('#5e2228', '#d22a2c', '#9b2a30', '#c80010',
                     '#6a1f25', '#d72d2b', '#5b2c2f', '#387448',
                     '#c0c5ba', '#888980', '#344039', '#4f4c3c',
                     '#807f67', '#386350', '#387448', '#5b6242',
                     '#669b3e', '#808572', '#7fb7b7', '#53636b',
                     '#85b3c1', '#507b8b', '#2c6195', '#4b5f71',
                     '#4b5f71', '#3f6698', '#26657f', '#398b98',
                     '#ddca72', '#c3b37d', '#d3bb95', '#c4bb9b',
                     '#a26540',
                     '#dbd5a5', '#a86428', '#c7a860', '#c0cc56',
                     '#e5e1d4', '#d3bb95', '#a26540', '#ead568',
                     '#7f5d47', '#b23a2d', '#c33431', 'd74122',
                     '#b23a2d'))

cas_plot_static <- ggplotly(cas_p_static) %>% 
                    partial_bundle() %>% 
                    toWebGL()

cas_p <- uo %>% 
  filter(college == 'College of Arts & Sciences' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  # geom_jitter(aes(color = as.factor(course_dept)), alpha = .1) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE, size = 1) +
  theme(legend.position = 'none') +
  scale_color_manual(values = c('#5e2228', '#d22a2c', '#9b2a30', '#c80010',
                                '#6a1f25', '#d72d2b', '#5b2c2f', '#387448',
                                '#c0c5ba', '#888980', '#344039', '#4f4c3c',
                                '#807f67', '#386350', '#387448', '#5b6242',
                                '#669b3e', '#808572', '#7fb7b7', '#53636b',
                                '#85b3c1', '#507b8b', '#2c6195', '#4b5f71',
                                '#4b5f71', '#3f6698', '#26657f', '#398b98',
                                '#ddca72', '#c3b37d', '#d3bb95', '#c4bb9b',
                                '#a26540',
                                '#dbd5a5', '#a86428', '#c7a860', '#c0cc56',
                                '#e5e1d4', '#d3bb95', '#a26540', '#ead568',
                                '#7f5d47', '#b23a2d', '#c33431', 'd74122',
                                '#b23a2d'))

cas_plot <- ggplotly(cas_p) %>% 
  partial_bundle() %>% 
  toWebGL()

subplot(cas_plot_static, cas_plot)

```

### College of Design

```{r}
cod_major <- c('Architecture' = '#FFF6B7',
               'Art' = '#8CD4C9',
               'Art History' = '#F7471A',
               'Historic Preservation' = '#D1E6F2',
               'Interior Architecture' = '#23A1E3',
               'Landscape Architecture' = '#AA1818',
               'Product Design' = '#601a35')

cod1 <- uo %>% 
  filter(college == 'College of Design' &
           ge_teach_fte < .5) %>%
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_jitter(aes(color = as.factor(course_dept)), alpha = .1) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE, size = 1.25) +
  scale_colour_manual(name = "course_dept",values = cod_major) +
  xlim(0.0, .5) +
  labs(title = 'Association between GE Teaching FTE\nand Undergraduate Credit Hours',
       subtitle = 'for College of Design',
       x = 'GE Teaching FTE',
       y = 'Undergraduate Credit Hours') +
  theme(legend.position = 'none')

cod2 <- uo %>% 
  filter(college == 'College of Design' &
           ge_teach_fte < .5) %>%
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  # geom_jitter(aes(color = as.factor(course_dept)), alpha = .1) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE, size = 1.25) +
  scale_colour_manual(name = "course_dept",values = cod_major) +
  xlim(0.0, .5)  +
    labs(title = 'Association between GE Teaching FTE\nand Undergraduate Credit Hours',
       subtitle = 'for College of Design',
       x = 'GE Teaching FTE',
       y = 'Undergraduate Credit Hours')

ggarrange(cod1, cod2, common.legend = FALSE)

```

### College of Education

```{r}
coe_major <- c('Counseling Psychology & Human Services' = '#669b3e',
               'Education Studies' = '#d72d2b',
               'Educational Methodology, Policy, & Leadership' = '#398b98',
               'Special Education & Clinical Sciences' = '#ea5227')

coe1 <- uo %>% 
  filter(college == 'College of Education' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_jitter(aes(color = as.factor(course_dept)), alpha = .1) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE, size = 1.25) +
  scale_color_manual(values = coe_major) +
  xlim(0.0, .5) +
  labs(title = 'Association between GE Teaching FTE\nand Undergraduate Credit Hours',
       subtitle = 'for College of Education',
       x = 'GE Teaching FTE',
       y = 'Undergraduate Credit Hours') +
  theme(legend.position = 'none')

coe2 <- uo %>% 
  filter(college == 'College of Education' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  # geom_jitter(aes(color = as.factor(course_dept)), alpha = .1) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE, size = 1.25) +
  scale_color_manual(values = coe_major) +
  xlim(0.0, .5) +
    labs(title = 'Association between GE Teaching FTE\nand Undergraduate Credit Hours',
       subtitle = 'for College of Education',
       x = 'GE Teaching FTE',
       y = 'Undergraduate Credit Hours')

ggarrange(coe1, coe2, common.legend = FALSE)
```

### Lundquist College of Business

```{r}

uo %>% 
  filter(college == 'Lundquist College of Business' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_jitter(aes(color = as.factor(course_dept)), alpha = .1) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE, size = 1.25) +
  xlim(0.0, .5) +
  scale_color_manual(values = c('#398b98')) +
  # annotate('text', x = .2, y = 130, label = 'Business Administration') +
  labs(title = 'Association between GE Teaching FTE\nand Undergraduate Credit Hours',
       subtitle = 'for Business Administration',
       x = 'GE Teaching FTE',
       y = 'Undergraduate Credit Hours') +
    theme(legend.position = 'none')

```

### School of Journalism & Communication

```{r}

uo %>% 
  filter(college == 'School of Journalism & Communication' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_jitter(aes(color = as.factor(course_dept)), alpha = .1) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE) +
  labs(title = 'Association between GE Teaching FTE\nand Undergraduate Credit Hours',
       subtitle = 'for Journalism',
       x = 'GE Teaching FTE',
       y = 'Undergraduate Credit Hours') +
  theme(legend.position = 'none') +
  scale_color_manual(values = c('#398b98')) +
  annotate('text', x = .2, y = 120, label = 'Journalism')

```

### School of Law

```{r}

uo %>% 
  filter(college == 'School of Law' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_jitter(aes(color = as.factor(course_dept)), alpha = .1) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE) +
  labs(title = 'Association between GE Teaching FTE\nand Undergraduate Credit Hours',
       subtitle = 'for Law',
       x = 'GE Teaching FTE',
       y = 'Undergraduate Credit Hours') +
  theme(legend.position = 'none') +
  scale_color_manual(values = c('#398b98')) +
  annotate('text', x = .3, y = 245, label = 'Law')

```

### School of Music & Dance

```{r}

uo %>% 
  filter(college == 'School of Music & Dance' &
           ge_teach_fte < .5) %>% 
  drop_na(ge_teach_fte, credit) %>% 
  ggplot(aes(ge_teach_fte, credit)) +
  geom_jitter(aes(color = as.factor(course_dept)), alpha = .1) +
  geom_smooth(aes(color = as.factor(course_dept)), method = 'lm', se = FALSE) +
  labs(title = 'Association between GE Teaching FTE\nand Undergraduate Credit Hours',
       subtitle = 'for Music',
       x = 'GE Teaching FTE',
       y = 'Undergraduate Credit Hours') +
  theme(legend.position = 'none') +
  scale_color_manual(values = c('#398b98')) +
  annotate('text', x = .1, y = 45, label = 'Music')

```

Row 
-----------------------------------------------------------------------

### Average GE Teaching FTE & Undergraduate Course Credits

```{r}

uo %>% 
  filter(ge_teach == 1) %>% 
  drop_na(ge_teach, ge_teach_fte, credit) %>% 
  group_by(college, course_dept, ge_teach) %>%
  summarize(mean_fte = mean(ge_teach_fte),
         `GE Teaching Observations` = n(),
         mean_credit = mean(credit),
         mean_class_fte = mean(fte),
         `Average GE Teaching FTE` = round(mean_fte, 3),
         `Average Student Credit Hours` = round(mean_credit, 3),
         `Average Student Class FTE` = round(mean_class_fte, 3)) %>% 
  rename(College = college,
         `Course Department` = course_dept) %>% 
  ungroup() %>% 
  dplyr::select(College, `Course Department`, `GE Teaching Observations`, `Average GE Teaching FTE`,
                `Average Student Class FTE`, `Average Student Credit Hours`) %>% 
  reactable::reactable()

```

### Correlation Between Teaching GE FTE & Undergraduate Course FTE

```{r}
beta_func <- function (object){
    if (!"lm" %in% attr(object, "class")) 
        stop("object has to be of class lm")
    object$standardized.coefficients <- coef(object) * apply(as.matrix(model.matrix(object)), 
        2, function(x) sqrt(sum((x - mean(x, na.rm = T) * attr(attr(object$model, 
            "terms"), "intercept"))^2, na.rm = T)))/apply(as.matrix(model.frame(object)[, 
        1]), 2, function(x) sqrt(sum((x - mean(x, na.rm = T) * 
        attr(attr(object$model, "terms"), "intercept"))^2, 
        na.rm = T)))
    # attr(object, "class") <- c("lm.beta", "lm")
    return(object)
}

uo_lm_list <- uo %>% 
  drop_na(college, course_dept, credit, ge_teach_fte) %>% 
  group_by(college, course_dept) %>% 
  nest() %>% 
  mutate(lm_model = map(data, ~lm(credit ~ ge_teach_fte, data = .x)),
         lm_coefs = map(lm_model, coef),
         ge_teach_fte_b = map_dbl(lm_coefs, 2),
         betas = map_dbl(lm_model, ~beta_func(.x)$standardized.coefficients[2]),
         lm_r2 = map_dbl(lm_model, ~summary(.x)$r.squared),
         lm_pvalue = map_dbl(lm_model, ~summary(.x)$coefficients[, 4]['ge_teach_fte']),
         lm_r = map_dbl(lm_r2, ~sqrt(.x)))

uo_lm_list %>% 
  dplyr::select(college, course_dept, betas, lm_pvalue) %>% 
  rename(`College` = college,
         `Course Department` = course_dept) %>% 
  mutate(
    # b = round(ge_teach_fte_b, digits = 3),
         "\u03b2" = round(betas, digits = 3), 
         `p value` = round(lm_pvalue, digits = 3)) %>% 
  dplyr::select(
    # -ge_teach_fte_b, 
    -lm_pvalue, -betas) %>% 
  reactable::reactable()
```